\documentclass[10pt,A4paper]{article}
\usepackage[utf8]{inputenc}
\title{\bf{TrustFunds -\\
Decentralised Crowdfunding Platform on Blockchain}}
\author{Abraham V Shajan \and Alvin Varghese \and Amalia F \and Aswin U S 
\thanks {Project Guide: Prof. Nisha K K., Faculty, CSE, RIT-Kottayam}}
\date{\today}
\begin{document}
\maketitle
\vspace{-20pt}
\begin{center}
\section*{Abstract}
\end{center}

Our project, TrustFunds, aims to revolutionise the crowdfunding landscape by tackling persistent issues like fund misallocation, project delays, and fraudulent activities. We achieve this by creating a decentralised crowdfunding platform powered by Blockchain technology and smart contracts.
This platform streamlines fundraising for both fundraisers and backers, leveraging Blockchain technology to support socially and environmentally impactful projects, driving positive societal change. All transactions and funds are securely recorded on the Blockchain, ensuring the protection of user data and financial information.
TrustFunds also encourages continuous engagement between funders and backers, thus enhancing the chances of organisations achieving their environmental and social objectives through ongoing support and feedback.
In conclusion, the goal of TrustFunds is to revolutionise the crowdfunding industry by delivering an open, accessible, safe, automated and reliable crowdfunding platform. Utilising Blockchain and smart contract technology, we enable organisations to generate funds efficiently while protecting the integrity of campaigns.
\end{document}
